\documentclass[11pt,a4paper,sans]{article}
\title{Quest Commencement 2019}
\author{Leo Przybylski}
\begin{document}
\maketitle
\tableofcontents
\section{Prologue}
%% Introduction. About how life started for Ashley.

Thank you for coming together to give your support and encouragement, to 
bear witness to the graduation of the class of 2019, and to observe the 
next generation to carry on our values, past, present, and future all before God.
I'm not done yet, Ashley. Be patient. The enormity of the weight upon you will 
be more evident before I'm through. I jest.

Since the moment Ashley was born, my mortality has been ever present and obvious to me.
In \emph{that} moment, my wants and needs became a singular desire to show her the 
world as I knew it. To educate her and guide her on the path and the tools she would 
need for her journey as she proceeded to explore the newness of life and 
God's creation, and with every step make her mark upon it. I became changed. Call it 
baptism by afterbirth. The person I was before wouldn't recognize the person after.
My purpose was renewed. The life I promised to God, He now required for me teach His
newborn child.

\section{The Purpose of the Elders}
Our purpose in youth is to learn, to grow, and to become. To what do we strive toward?
Each of us is different in what God's will is for our lives, but we all come to a point
when we must--no, when we yearn by our programming to share our experiences, knowledge,
wisdom, skills, and shortcomings to those that would come after us.

\begin{quote}
    And God blessed them. And God said to them, “Be fruitful and multiply and fill the earth..."
    -- Genesis 1:28
\end{quote}

It isn't just our DNA that multiplies, but what we have collectively learned. Our programming 
compells us to advance ourselves and share. In that moment, I knew who I would be to her. 
Amongst also vowing to protect and secure her, to naively proclaim that no harm should ever befall
her in her life, I also promised beyond all else that she would come to understand through
me. It's impossible to be there for every step/misstep, fall, or first experience. I could never 
teach her human anatomy, parsing the human genome, calculating re-entry vectors for space capsules,
or the correct viscosity for hydraulic parts on a Mecha. I knew I needed to be there for the 
important moments to teach her how to live. Those moments when we pass on our values. The 
teachable moments when she would be in an ethical dilemma like chosing iOS or Android. 
The difficult moments that determine who we really are.

Now here we are. We never stop learning. Also, I am sure that I will have plenty of opportunities
to encourage, support, teach, and discipline Ashley for. Nevertheless, as her teacher, my time
is now over. It is my blessed honor that you all are here for this final lesson before Ashley
continues on to the next stage in her life.

\section{Lessons Learned}
Before that last lesson, I'd like to go over a couple that we had gone over in the past and
finish them.

\subsection{Fail Fast}
Albert Einstein, Abraham Lincoln, Henry Ford, Colonel Sanders, Bill Gates, Dr. Seuss, 
George Lucas, Michael Jordan, Elon Musk, and Tony Stark are all successful failures. Yes, I 
realize Tony Stark isn't a real person. 

Do not be afraid of failure. Neither failing or becoming publicly recognized as a failure 
should ever cause you to compromise what you know you must do. 

\begin{quote}
    Around here, however, we don't look backwards for very long. We keep moving
    forward, opening up new doors and doing new things because we are curious, and
    curiosity keeps leading us down new paths. Keep moving forward --Walt Disney
\end{quote}

Fail quickly, and fail often because the road to success is paved by failure. The more ofte
you fail and pick yourself back up, the faster you will reach success. When you fail, fail so 
epicly that your name will reknown in revel and glory. Let it be a such a failure people remember 
because your success will be that much more glorious.


\subsection{Stick to the Plan}
Ashley's education has taken on a number of themes. None summarized it more than uncertainty.
As a result, over the years, Jeremiah 29:11 has become our creed. During those moments when 
purpose was unclear. Continuing was regarded as futile. It is hard to imagine looking back on
the past that things had ever come to such a point. We learned to weather the difficult times
and that we need to "Stick to the Plan". 

It's only when we leave the plan that things get really bad.

\begin{quote}
    "And we know that for those who love God all things work together for good, for those who 
    are called according to his purpose." Romans 8:28
\end{quote}

\begin{quote}
    "But, as it is written, “What no eye has seen, nor ear heard, nor the heart of man imagined, what God has prepared for those who love him” 1 Corinthians 2:9
\end{quote}


\subsection{Be Not a Fool}

This is familiar to Ashley because I am outspoken of how much I value wisdom
in not speaking. 
\begin{quote}
    "A fool gives full vent to his spirit,
but a wise man quietly holds it back." Proverbs 29:11
\end{quote}

\begin{quote}
    "Do you see a man who is hasty in his words?
There is more hope for a fool than for him." Proverbs 29:20
\end{quote}

\subsection{Put God First}
\begin{quote}
    "Trust in the Lord with all your heart, and do not lean on 
your own understanding. In all your ways acknowledge him, and 
he will make straight your paths." -- Proverbs 3:5-6
\end{quote}

Faith was a cornerstone for Ashley as she grew older. I emphasized this
to her continuously through the importance of putting God first in our lives.
Our faith becomes manifest through our thoughts and actions.

\begin{quote}
    "Whatever you do, work heartily, as for the Lord and not for men" -- Colossians 3:23
\end{quote}

Giving your all needs to be a priority especially when no one is watching. In the 
end, we live not for ourselves, but for God.


\section{Epilogue}
%% Conclusion. About the future and what to look forward to

\subsection{Never Deny Yourself}
This is it. "nosce te ipsum" know thyself by Plato and Socrates. Remember who you
are and never compromise that for anything. Never compromise your values or what makes
you you.


    \begin{quote}
        "Do not be conformed to this world, but be transformed by the renewal of your mind, that by testing you may discern what is the will of God, what is good and acceptable and perfect." Romans 12:2
    \end{quote}

Subvert expectations. People will judge you by your age, looks, manner, or even the way you
speak. Show them that the rules do not apply to you, that you are special, and you belong to 
God.


God calls us to do the hard thing. Often times, the path to least resistence
is the wrong path. The world is full of people who epitomized cliches simply by 
chosing the easier way. I am not saying you should choose the hard thing because it's
hard. I'm saying the choice to do the right thing itself should be hard. Ultimately,
decisisons like this cannot be made alone.

\begin{quote}
    "Listen to advice and accept instruction,
that you may gain wisdom in the future." Proverbs 19:20
\end{quote}

Therefore, do not choose to be alone. Lean on others, especially lean on God. 
Never forsake him.

\subsection{Conclusion}

With that, I conclude that you have now surpassed what I have left to teach. 

Ashley has always learned quickly. She has accomplished much. She is a capable artist,
pianist, and literate in most technology. Ashley has also an accomplished athlete.
It is pretty common to hear me say for no reason at all, "I made that." in pride for 
what Ashley has accomplished as a scholar and a woman. Go forth
and be a good testimony to others giving glory to God. Remember you are an extension 
of myself.


\end{document}